Data preparation for employee category analysis

### 2023-04-19 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Developed person-level who period aggregates

@@

```{r}
cohort_ids %>% 
  summarise(n_distinct(person_id)) %>% 
  pull() ==
  cohort_first %>% 
  summarise(n_distinct(person_id)) %>% 
  pull()
````

@@

```{r}
cohort_panel %>% 
  summarise(working_days = n_distinct(date)) %>% 
  ungroup()
```

```{r}
cohort_panel %>% 
  group_by(person_id) %>% 
  filter(daily_status_imputed != "Leave") %>% 
  summarise(working_days = n_distinct(date)) %>% 
  ungroup()
```

```{r}
cohort_panel %>%
  mutate(daily_status_imputed = factor(daily_status_imputed)) %>% 
  group_by(person_id,daily_status_imputed,.drop = FALSE) %>% 
  summarise(working_days = n_distinct(date)) %>% 
  ungroup() %>% 
  pivot_wider(values_from = working_days, names_from = daily_status_imputed) %>% 
  clean_names() %>% 
  rename_with(~glue::glue("daily_status_imputed_{.}"), -person_id)
```

@@

@@

```{r}
unique_email_base == unique_email_building
```
Review.

>>>>

Updated data type for check-in status.

```{r}
check_in_panel <- 
  check_in_panel %>% mutate(
    daily_status_imputed = factor(daily_status_imputed),
    daily_status_imputed =
      fct_recode(daily_status_imputed,
                 permanent_departure = "This employee is no longer with the agency (retired, resigned, or other form of permanent departure)")
  )
```

@@

```{r}
cohort_ids %>% 
  summarise(n_distinct(person_id)) %>% 
  pull() ==
  cohort_first %>% 
  summarise(n_distinct(person_id)) %>% 
  pull()
```

Set up `prep_building`.

```{r}
prep_building <- 
  cohort_ids
```

@@

### Employee, whole period variables

For following variables are aggregated for the whole period for each employee:

@@

First, calculating the number of days in the observation window.

```{r}
observation_window_days <- 
  cohort_panel %>% 
  summarise(observation_window_days = n_distinct(date)) %>% 
  ungroup() %>% 
  pull()

observation_window_days
```

Now calculating the number of days per employee by `daily_status_imputed`. Proportions are caluculated for onsite and telework only. The calculations are made in two ways in two ways. First as a proportion of employee working days:

$$
\frac{DailyStatusDays}{WorkingDays}
$$

where

$$
WorkingDays = OnsiteDays + TeleworkDays
$$

Second as a proportion of days in the observations window:

$$
\frac{DailyStatusDays}{ObservationWindowDays}
$$

```{r}
prep_xx <- 
  cohort_panel %>%
  group_by(person_id,daily_status_imputed,.drop = FALSE) %>% 
  summarise(working_days = n_distinct(date)) %>% 
  ungroup() %>% 
  pivot_wider(values_from = working_days, names_from = daily_status_imputed) %>% 
  clean_names() %>% 
  rename_with(~glue::glue("daily_status_{.}"), -person_id) %>% 
  mutate(
    working_days = daily_status_reporting_to_job_site + daily_status_teleworking,
    daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
    daily_status_teleworking_working_prop = daily_status_teleworking/working_days,
    daily_status_reporting_to_job_site_observation_prop = daily_status_reporting_to_job_site/observation_window_days,
    daily_status_teleworking_observation_prop = daily_status_teleworking/observation_window_days
  ) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

Review data.

```{r}
prep_xx %>% 
  skim()
```
Check: These have the same number of unique `person_id`.

```{r}
cohort_ids %>% 
  summarise(n_distinct(person_id)) %>% 
  pull() ==
  prep_xx %>% 
  summarise(n_distinct(person_id)) %>% 
  pull()
```

Join to `prep_building`.

```{r}
prep_building <- 
  prep_building %>% 
  left_join(prep_xx)
```

```{r}
prep_xx %>% 
  pivot_longer(-person_id) %>% 
  filter(str_detect(name, "_prop")) %>% 
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(facets = vars(name))
```

@@
